ZCB Pricing

### 2018-07-05 ZCB Pricing .Rmd
Modifications to the implicit method
Addition of the Crank-Nicholson Method

# Simple Bond price function
B <- function(t,r){
  exp(-(T-t)*r)
}

@@

```{r 5}
# Implicit Method
# Implicit Method

@@

  pm <- function(j){
    dt*(J[j+1] + 1/dt)
  }

@@

```{r 6}
# Crank-Nicholson Method
```

>>>>

# Simple Bond price function
B <- function(t,T,r){
  exp(-(T-t)*r)
}

@@

```{r 5}

# Implicit Method

@@

  pm <- function(j){
    dt*(J[j+1] + 1/dt +sigma^2/(dr^2))
  }

@@

```{r 6}
# Crank-Nicholson Method

CN <- function(alpha, beta, sigma, r, I, J){
  # I = partition of time interval
  # J = partition of short rate interval

  X <- length(I) # number of time grid points
  Y <- length(J) # number of rate grid points

  nr <- Y - 1 # number of rows

  dr <- J[2] - J[1]
  dt <- 1/X

  #===========================================================================================
  # Define the following functions for j = 1,...,nr at each time point i

  pd <- function(j){
    (alpha -beta*J[j+1])/(2*dr) - sigma^2/(4*dr^2)
  }

  pm_1 <- function(j){
    J[j+1]/2 + 1/dt + sigma^2/(2*dr^2)
  }

  pm_2 <- function(j){
    -J[j+1]/2 + 1/dt - sigma^2/(2*dr^2)
  }

  pu <- function(j){
    - (alpha -beta*J[j+1])/(2*dr) - sigma^2/(4*dr^2)
  }

  #===========================================================================================
  # Define 2 tridiagonal matricies. One for time point i and one for time point i+1

  Diag_1 <- matrix(0,nrow = nr,ncol = nr)
  Diag_2 <- matrix(0,nrow = nr,ncol = nr)

  # Main diagonal of matrix 1
  for (j in 1:nr){
    Diag_1[j,j] <- pm_1(j)

  # Filling lower diagonal of matrix 1
  for (j in 2:nr){
    Diag_1[j,j-1] <- pd(j)
  }

  # Filling upper diagonal of matirx 1
  for (j in 1:(nr-1)){
    Diag_1[j,j+1] <- pu(j)
  }

  # Main diagonal of matrix 2
  for (j in 1:nr){
    Diag_2[j,j] <- pm_2(j)

  # Filling lower diagonal of matrix 2
  for (j in 2:nr){
    Diag_2[j,j-1] <- -pd(j)
  }

  # Filling upper diagonal of matirx 2
  for (j in 1:(nr-1)){
    Diag_2[j,j+1] <- -pu(j)
  }

  #===========================================================================================
  # Constructing more matricies and iterating the procedure from maturity to time 0
  # These matricies take care of the boundary conditions
  C_1 <- matrix(0,nrow = nr,ncol = 1)
  C_1[1,1] <- pd(1)
  C_1[nr,1] <- pu(nr)

  C_2 <- matrix(0,nrow = nr,ncol = 1)
  C_2[1,1] <- -pd(1)
  C_2[nr,1] <- -pu(nr)

  # Vector of bond price values at time i
  Bond_values <- matrix(1,nrow = nr, ncol = 1)

  for (i in I){
    Inv <- solve(Diag_1)
    RHS <- Diag_2%*%Bond_values + C_2 - C_1
    Bond_values <- Inv%*%RHS
  }

  Bond_values

G <- CN(0.08,0.8,0.005,0.05,I=1:1000, J = seq(0,0.10,0.01))
